The demographic costs of sexually antagonistic selection in partially selfing populations

### 2021-12-20 doc/ResponseLetter-R1.tex

\begin{quote}
	{\itshape We have added a sentence earlier in this paragraph where we remind readers what dioecy is ({\bf L.54}). Hermaphroditism is defined earlier in the paragraph, so an additional reference seemed redundant.}
\end{quote}

@@

- Line 80: just a few words to clarify "obligate outcrossing" (something like (no selfing allowed) maybe)

\begin{quote}
	{\itshape Fixed ({\bf L.103-104}).}
\end{quote}

- Line 233: f and f’ are called "adult fertilities". However, they correspond to that rate only for certain specific genotypes. Maybe clarify that by calling them "adult maximum fertilities" ?

\begin{quote}
	{\itshape Good point, fixed ({\bf L.161, 185}).}
\end{quote}

@@

- Results: it took me a while to figure out Fig 1 (mainly because I was looking at it in B and W). I am just wondering whether it would be easier to read with only one f per chart. Maybe as a separate chart that illustrates the general shape of the parameter space for polym * extinction for only one C, one h and one f... then followed by these 6 graphs as they are now.

\begin{quote}
	{\itshape We want to thank the reviewer for this suggestion. We now start with a figure that only has one f, and that separately explains what happens to the allele frequencies (Population genetic outcome) and to the population growth rate (Demographic Outcome), see new {\bf fig. 1}. We hope that this will make it easier to interpret the old fig. 1, which is now {\bf fig. 2}. We have also included a new supplementary figure, {\bf fig. S1}, with detailed heatmaps for each of the parameter combinations presented in the this figure (i.e., one $f$ per panel). However, we felt that this revised figure was to large and complicated to present in the main text (18 vs. 6 panels).}
\end{quote}

\noindent-- Maybe mention once, in a few words, what is meant by "segregate as a diallelic locus".
\begin{quote}
	{\itshape We have added a brief parenthesis to clarify ({\bf L.434--435}).}
\end{quote}

@@

\noindent-- Fig 4 : they are supposed to be dashed lines and dotted lines but all I see are dashed lines with various dashes. I found 4B in particular, hard to understand at first sight.

\begin{quote}
	{\itshape This figure now appears as four separate heatmaps, each with one set of invasion conditions ({\bf fig.~5}). We hope this eases interpretation of the figure.}
\end{quote}
\bigskip

@@

\noindent-- The 0s representing 0 matrices in eq 5 are not bold
\begin{quote}
	{\itshape Fixed}
\end{quote}

\noindent-- In same equation 1w is not defined
\begin{quote}
	{\itshape Fixed}
\end{quote}

\noindent-- Line 142, 2 "the"s
\begin{quote}
	{\itshape Fixed}
\end{quote}

\noindent-- Line 553 : not a typo, but the "was that how" in the middle of the sentence makes it hard to read
\begin{quote}
	{\itshape We have re-written this sentence to avoid this awkward phrasing ({\bf L.579--580}).}
\end{quote}
